%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Friggeri Resume/CV
% XeLaTeX Template
% Version 1.0 (5/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Adrien Friggeri (adrien@friggeri.net)
% https://github.com/afriggeri/CV
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX and the bibliography, if used,
% needs to be compiled with biber rather than bibtex.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{friggeri-cv} % Add 'print' as an option into the square bracket to remove colors from this template for printing

\begin{document}

\header{}{Cathal Garvey}{Synthetic Biologist, Science Communicator} % Your name and current job title/field

%----------------------------------------------------------------------------------------
%	SIDEBAR SECTION
%----------------------------------------------------------------------------------------

\begin{aside} % In the aside, each new line forces a line break
\section{contact}
22 McDonagh Road,
Ballyphehane,
Cork
~
+353 (0) 87 6363185
~
\href{mailto:cathalgarvey@cathalgarvey.me}{cathalgarvey@cathalgarvey.me}
\href{http://www.indiebiotech.com}{indiebiotech.com}
\href{https://www.github.com/cathalgarvey}{github.com/cathalgarvey}
~
\section{research}
Lean Biotech R\&D
Science Communication
Computational Biology
Synthetic Biology
Precision Gene Therapy
~
\section{programming}
Python, Lua, Coffeescript, Javascript, CSS3 \& HTML5, Mozilla Rust, Haxe, Java, Cobra (CLI), Haskell, ANSI\,C
~
\section{interests}
Synthetic Biology, Biotech, Bioinformatics, Programming, Gene Therapy, Cancer, Ageing, Cryptography, Data Analysis \& Visualisation, Open Science, Permaculture, Cycling, Writing, Hiking, Linux \& FLOSS
%----------------------------------------------
\end{aside}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Formal Education}

\begin{entrylist}
%------------------------------------------------
\entry
{2003--2007}
{Bachelor of Science, Genetics}
{NUI-Cork / University College Cork}
{Focus on Medical Genetics, Bioethics, Virology \& Plant Science.
Penultimate year project on plant immune response and soil potentiation of plant
disease resistance. Final year project on murine pregnancy-specific glycoproteins \&
PCR recovery of same. Graduated 2H1 with consistent honours.
}

\end{entrylist}
%------------------------------------------------

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{Professional Experience}

\begin{entrylist}
%------------------------------------------------
\entry
{2012--2014}
{Glowbiotics Ltd}
{Cork, Ireland}
{\emph{Founder, Chief Executive Officer} \\
Two years in a venture-funded startup pioneering lean biotechnology and computational
DNA design for synthetic biology. Wrote a number of in-house DNA design tools, designed
and used in-house hardware designs to reduce costs and accelerate research. Collated
and compiled protocols and SOPs based on deep literature research that saved time
and money while remaining efficient and reliable. Conceived and designed a series of
ambitious DNA-based products with many novel and positive results.
}
%------------------------------------------------
\entry
{2014}
{Open Innovation Partners Ltd}
{Cork, Ireland}
{\emph{Contract Software Engineer} \\
Contracted to produce a business intelligence \& data-visualisation platform for co-authorship
data via the NCBI EUtils API in order to perform due diligence consultations and to discover
and assess potential future academic collaborators. Given a name or a MeSH heading, a
connectivity graph with visual indicators of academic impact could be produced and interactively
explored. Also offered incidental support in data recovery, analysis \& databasing.
}
%------------------------------------------------
\entry
{2013--2014}
{Science Gallery}
{Trinity College, Dublin, Ireland}
{\emph{Exhibit Curator} \\
Co-curated a flagship exhibit exploring the future and cultural role of Synthetic
Biology. Assisted in selecting, coaching and properly exhibiting pieces exploring
democratisation of science, speculative med-tech design, trans-humanism and radical
or guerilla bioremediation. Provided a number of workshops and residencies on synthetic
biology \& genetics.
}
%------------------------------------------------
\entry
{2007--2010}
{Cork Cancer Research Centre}
{Cork, Ireland}
{\emph{Research Assistant} \\
DNA design, cloning \& artificial gene synthesis for gene therapy vectors.
PCR optimisation vector insert recovery using stepdown and solvated PCR.
Academic review support for projects related to targeted, integrative gene therapy.
Received training in mammalian cell culture, laboratory animal welfare \& handling.
Received, processed \& stored a number of primary human tissue samples for research use.
Conducted gene therapy trials on in-vitro mammalian cell cultures.
Maintained diverse mammalian cell culture stocks in nitrogen and in constant passage. 
}
%------------------------------------------------
\end{entrylist}

\pagebreak
%----------------------------------------------------------------------------------------
%	MEMBERSHIPS SECTION
%----------------------------------------------------------------------------------------

\section{Memberships}

\begin{entrylist}
%------------------------------------------------
\entry
{2014}
{Secretary}
{Cork Biomakerspace}
{\emph{(In progress)} Founding, locating and outfitting a biolab suitable for
community, outreach, educational and start-up use in Cork City Centre with support
from local industry, academia and state bodies.
}

%------------------------------------------------
\entry
{2012--2014}
{Leonardo}
{Science Gallery "Leonardo" Group, Trinity College Dublin}
{Serving as member of Leonardo think-tank, providing support and creative input on
present and future exhibits, knowledge and input to events, membership on various
panels and suggestions for collaborations and future exhibit curators.
}
%------------------------------------------------
\entry
{2009-2014}
{Founder}
{Nexus Cork Makerspace}
{Founded a successful information technology club which has held stable residence
in a central location and which has hosted a variety of technology related events.
}
%------------------------------------------------
\entry
{2011}
{Delegate}
{DIYbio.org Bioethics Congress}
{Participated in creating a widely accepted, terse yet expressive code of conduct
for independent researchers and amateur biotechnologists.
}
%------------------------------------------------
\end{entrylist}

%----------------------------------------------------------------------------------------
%	SOFTWARE SECTION
%----------------------------------------------------------------------------------------

\section{Software}

\begin{entrylist}
%------------------------------------------------
\entry
{2012}
{\href{https://github.com/cathalgarvey/pysplicer}{PySplicer}}
{Github}
{Wrote a cutting edge CDS optimisation suite, PySplicer, which implements current
research in codon and coding sequence optimisation, surpassing all other freely available tools.
Used in-house to design fluorescent protein expression constructs successfully, 
with exceptional expression levels.
}
%------------------------------------------------
\entry
{2013}
{\href{https://github.com/cathalgarvey/dncode}{DNcode}}
{Github}
{Wrote a compression function for nucleotide sequences which could rapidly \& 
losslessly compress DNA or RNA sequences to one quarter of their original storage 
size, at a scalar rate that could easily be implemented at database level without 
significant performance loss. Applications for bioinformatic servers or for 
archival use on growing bodies of medical sequence data.
}
%------------------------------------------------
\entry
{2013}
{Litmoria}
{Private / Proprietary}
{Wrote a search-engine and data-visualisation framework for academic data, graphing
co-authorship connectivity, authorship volume, last-author frequency, \& degree-of-separation
for data from NCBI Pubmed. The engine allows arbitrary search patterns by author name
or by keyword, and has been instrumental to the client in evaluating potential academic
partners, as well as seeking unaffiliated yet academically well-placed partners for
due-diligence prior to investment or partnerships.
}
%------------------------------------------------
\end{entrylist}

%----------------------------------------------------------------------------------------
%	HARDWARE SECTION
%----------------------------------------------------------------------------------------
\pagebreak

\section{Hardware}
\begin{entrylist}
%------------------------------------------------
\entry
{2009}
{\href{https://github.com/cathalgarvey/dremelfuge}{Dremelfuge}}
{Github}
{Having a need of a centrifuge for work in my own lab, and perceiving a general
need for a low-cost, high-speed microcentrifuge for medical applications in deprived
areas, I designed a 3D-printable rotor for common rotary multitools which could be
fabricated for approximately \euro1 and which could easily accomplish routine medical and
laboratory centrifugation. The designs were made available generally, and have been
exceptionally well received.
}

\entry
{2011}
{PID Water Bath Controller}
{Private Implementation}
{Needing a water-bath and scandalised by the prices quoted for such a simple piece
of equipment, I designed a microcontroller-driven feedback system and AC power controller
which could be used with domestic equipment (to wit, a kettle) to provide a water bath
solution for general use. Upgrade to an edge-immersion, fan-agitated system was partially
implemented but was found to be unnecessary.
}

\entry
{2012}
{\href{https://github.com/cathalgarvey/openpycr}{OpenPyCR}}
{Github}
{For reasons of cost-effectiveness and ease of customisation, I made use of an OpenPCR
thermal cycler for polymerase chain reaction and other enzymatic or cell reactions requiring
precise timing and temperature control. However, the software provided was poorly customisable
and required software I was unwilling to install for security reasons, so I re-implemented
the hardware control software from first principals, and extended it to allow a terse and
human-readable specification of program flow in plain text.
}

\end{entrylist}

%----------------------------------------------------------------------------------------
%	BIOTECH SECTION
%----------------------------------------------------------------------------------------

\section{Biotech}
\begin{entrylist}
%------------------------------------------------
\entry
{2010}
{IndieBB (1)}
{Glowbiotics}
{Identifying a market need for a robust \& modern-standards compliant plasmid vector
for \emph{B.subtilis}, I designed a vector entirely manually which would enable
antibiotic-free selection \& maintenance and which provided "biobrick" compatible
cloning sites. The selection scheme, which relied upon sugar to transiently complement
lab strains' inability to differentiate into swarming cells, worked as intended but
the plasmid vector itself proved unstable; I would later learn that the CDS optimisation
systems I was using were just becoming deprecated with new research, leading to the
authorship of \emph{PySplicer}, above.
}

\entry
{2012-2013}
{Fluorenzymes}
{Glowbiotics}
{Desiring to produce and market a "ferment your own" enzyme product which would permit
arbitrary enzyme fermentation and purification in usefully pure form, I designed a novel
chromatographic solution and tested it with transgenic fluorescent proteins. Wild-Type
GFP was optimised for expression in \emph{E.coli} using in-house software \emph{PySplicer}
and was fused to a likewise optimised CDS coding for an agarose-binding protein domain, to
provide an agar or agarose-based chromatographic separation and purification method.
While proper function of PySplicer was successfully demonstrated by vivid, eGFP-like
fluorescence (a remarkable achievement for wild-type GFP), and while successful export
of some protein to \emph{E.coli} periplasm was achieved using a fusion export system,
the agarose-binding protien proved unamenable to protein fusion and did not function as
a chromatographic fusion tag after several rounds of prototyping and expert consultation.
}

\entry
{2014}
{IndieBB (2)}
{Glowbiotics}
{Returning to the need for a generalised, modern vector for biotechnology that obviated
the need to rely on antibiotics for selection and maintenance, I designed a concept
vector that would enable antibiotic-free selection in \emph{E.coli} using Colicin-V
mediated allelopathic selection. Planned further experiments upon the vector would have
attempted to replace the sizeable transport cassettes of the Colicin V operon with
low-cytotoxicity periplasmic disruption proteins, which could potentially have yielded
allelopathic selection with a lower DNA footprint than extant optimised AmpR cassettes.
Regrettably, funding was not raised for this project, though it is instead being implemented
as an iGEM project by a New York biotechnology lab.
}

\end{entrylist}

%----------------------------------------------------------------------------------------
%	COMMUNICATION SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{Communication Events}

\begin{entrylist}
%------------------------------------------------
\entry
{2014}
{\href{http://www.pintofscience.ie}{Stem Cells, Biohacking, GM \& the future of humans}}
{Pint of Science, Dublin}
{Participated in a Panel Discussion on Biotechnology, Agriculture, Bioethics \& Human Enhancement
with positive responses from a mixed-background audience. 
}
%------------------------------------------------
\entry
{2013}
{\href{https://www.youtube.com/watch?v=g_ZswrLFSdo}{Bringing Biotechnology Into the Home}}
{TEDx Dublin 2013}
{Presented a vision for ubiquitous synthetic biology as a facet of a future everyday life at
an event attended by thousands and viewed and favoured by over ten thousand more since.
}
%------------------------------------------------
\entry
{2012}
{\href{http://vimeo.com/51144273}{Enter Bio-Hacking}}
{PICNIC Conference, Amsterdam}
{Introduced the rapidly changing field of "do-it-yourself" biotechnology at a technology
and design conference in a prominent waterfront theatre in Amsterdam.}
%------------------------------------------------
\end{entrylist}

%----------------------------------------------------------------------------------------
%	MEDIA APPEARANCES SECTION
%----------------------------------------------------------------------------------------

\section{Media Appearances}

\begin{entrylist}
%------------------------------------------------
\entry
{2012}
{\href{http://www.technologyreview.com/news/426885/doing-biotech-in-my-bedroom/}{Doing Biotech in my Bedroom}}
{MIT Technology Review}
{Coverage of a lab I established in a domestic setting and my work in enabling 
low-cost synthetic biology. (NB: There was never a bed in the lab)
}
%------------------------------------------------
\entry
{2012}
{\href{http://www.nytimes.com/2012/01/17/science/for-bio-hackers-lab-work-often-begins-at-home.html?_r=0}{For Bio-hackers, Lab Work Often Begins at Home}}
{New York Times}
{Headed a story on DIY-biotechnology with reference to my work designing low-cost tools and methods.
}
%------------------------------------------------
\entry
{2013}
{Biohackers - Les Bricoleurs d'ADN}
{Le Monde (Online)}
{Presented alongside other leading figures in Lean Biotech in an interactive online
format which encouraged viewers to "ask" questions and receive pre-recorded responses.
Initially available to the public, but since paywalled. 
}
%------------------------------------------------

\end{entrylist}


\end{document}
